FictionEro - Affective Impact of Fiction

### 2025-09-15 analysis/analysis.qmd
minor

@@

table_dvour <- function(g) {
  performance::performance_dvour(g) |> 
    arrange(desc(D_vour)) |> 
    gt::gt() |> 
    gt::data_color("D_vour", palette = "green", domain = c(0, 1)) |> 
    gt::fmt_auto()
}

g1 <- modelbased::estimate_grouplevel(arousal1)
table_dvour(g1)

>>>>

- Reliability

```{r}
table_dvour <- function(g) {
  performance::performance_dvour(g) |> 
    arrange(desc(D_vour)) |> 
    gt::gt() |> 
    gt::data_color("D_vour", palette = "green", domain = c(0, 1)) |> 
    gt::fmt_auto()
}

g1 <- modelbased::estimate_grouplevel(m_a2, type = "total")
table_dvour(g1)

@@

colors <- c("p" = "#9C27B0", "confright" = "#795548", "confleft" = "#795548",
            "precright" = "#607D8B","precleft" = "#607D8B", "pex" = "#FF9800", "bex" = "#F44336")

p2_dvour <- g1_choco |> 
  mutate(Component = ifelse(Component == "conditional", "p",  Component),
         Component = fct_relevel(Component, "p", "confright", "confleft", "precright", "precleft", "pex", "bex"),
         Group = fct_relevel(Group, "Participant", "Item"),
         .group = paste0(Group, " (", Component, ")")) |>
  ggplot(aes(x = Median, y = Level)) +
  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color= Component), linewidth = 0.3, size = 0.05) +
  facet_grid(Group~Component, scales = "free", switch="both") +
  ggside::geom_xsidedensity(aes(group = .group, fill = Component), color = NA) +
  ggside::ggside(scales  = "free") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        strip.placement.x = "outside",
        strip.background = element_rect(fill = NA, color = NA),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major.y = element_blank(),
        legend.position = "none")
p2_dvour
```
